---
title: "FinalProject_WordEmbeddings"
author: "Katharyn Loweth"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## word embeddings

reducing dataframe to only include documents that include at least one of they keywords for analysis

taking out data and evaluation because of their frequency in the dataframe plus being reflected in other keywords

```{r}
library(tidyverse) # loads dplyr, ggplot2, and others
library(stringr) # to handle text elements
library(tidytext) # includes set of functions useful for manipulating text
library(text2vec) # for word embedding implementation
library(widyr) # for reshaping the text data
library(irlba) # for svd
library(here)
library(quanteda)
library(ggplot2)
library(conText)

```

```{r}
setwd("/Users/katharynloweth/Desktop/TextAsData/TAD_FinalProject")

#clearing environment
rm(list = ls())

#loading data
fed = read.csv("TAD_finalproject_corpus_FINAL.csv")
glimpse(fed)
#str(fed)
table(fed$president.identifier) #one bill clinton record
fed = fed %>% filter(fed$president.identifier != "william-j-clinton")
```

```{r}
#creating ID
fed$id <- 1:nrow(fed)

#changing format of date variable so that it is recognized as a date
fed$publication_date_ref = as.Date(fed$publication_date, "%Y-%m-%d")
#typeof(fed$publication_date_ref)
#head(fed$publication_date_ref)
fed$publication_year = format(fed$publication_date_ref, "%Y")
#head(fed$publication_year)
fed$publication_monthyear = format(fed$publication_date_ref, "%m-%Y")


fed = fed %>% mutate(presidential_term = case_when((publication_date_ref < as.Date("2005-01-20") & fed$president.identifier == "george-w-bush") ~ "Bush-1",
                                                   (publication_date_ref >= as.Date("2005-01-20") & fed$president.identifier == "george-w-bush") ~ "Bush-2",
                                                   (publication_date_ref < as.Date("2013-01-20") & fed$president.identifier == "barack-obama") ~ "Obama-1",
                                                   (publication_date_ref >= as.Date("2013-01-20") & fed$president.identifier == "barack-obama") ~ "Obama-2",
                                                   (publication_date_ref < as.Date("2021-01-20") & fed$president.identifier == "donald-trump") ~ "Trump-1",
                                                   (fed$president.identifier == "joe-biden") ~ "Biden", 
                                                   (publication_date_ref >= as.Date("2025-01-20") &fed$president.identifier == "donald-trump") ~ "Trump-2"), 
                     pres_party = case_when(fed$president.identifier %in% c("george-w-bush", "donald-trump") ~ "republican", fed$president.identifier %in% c("barack-obama","joe-biden") ~ "democrat"))

```

Creating corpus
```{r}
fed_corpus <- corpus(fed, text_field = "body_text")
#names(docvars(fed_corpus))

```

functions needed for code:
```{r}
remove_words = c("document", "section", "headings", "ii", "iii", "iv", "vi", "vii", "v","viii", "ix", "fuel_efficiency", "energy_efficiency")

junk_patterns <- c(
  "^[0-9]+$",              # pure numbers like 2020
  "^[0-9\\-]+$",           # numbers with dashes like 123-456
  "^[0-9]{3,}-[0-9]{3,}",  # phone-number-like patterns
  "^[^a-z]+$",             # non-alphabetic strings
  "^[a-z]*-[0-9a-z]+$",    # alphanumeric with dash like n-1a, abc-123
  "^[0-9a-z]+-[a-z]+$"     # variants like 1a-test or a1-b
)

prepping_tokens_we = function(c, words_to_remove, mtf, mdf){
  
  t = tokens(c, what = "word", remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_separators = TRUE) %>% tokens_tolower() %>% tokens_remove(pattern = junk_patterns, valuetype = "regex")
  f = dfm(t, verbose = FALSE) %>% 
  dfm_remove(c(stopwords(language = "en"), words_to_remove)) %>% 
  dfm_trim(min_termfreq = mtf, termfreq_type = "count", max_docfreq = mdf, docfreq_type = "prop") %>%
  featnames() 
  
  tokens_pad = tokens_select(t,
                            f,
                            padding = TRUE)
  return(tokens_pad)
}





glove_modeling = function(toks_feats, dimensions, window_size, fcm_type, n_iterations){
  glove <- GlobalVectors$new(rank = dimensions, #dim
                           x_max = 10,
                           learning_rate = 0.05)
  
  mat = fcm(toks_feats, 
                context = "window", 
                window = window_size, 
                count = fcm_type, 
                tri = FALSE)
  start = Sys.time()
  
  glove_fit = glove$fit_transform(mat, 
                               n_iter = n_iterations,
                               convergence_tol = 1e-3, 
                               n_threads = parallel::detectCores())
  end = Sys.time()
  
  print(end-start)
  
  
  word_vectors_context <- glove$components
  
  word_vectors <- glove_fit + t(word_vectors_context)
  return(word_vectors)
}






find_nearest <- function(word, pretrained_glove_model, top_n, pterm) {
  focusword = pretrained_glove_model[word, , drop = FALSE]
  n_words = find_nns(target_embedding = focusword, 
                     pre_trained = pretrained_glove_model, N = top_n + 1,
                     candidates = NULL, norm = "l2", stem = FALSE)
  n_words_df = as.data.frame(n_words) %>% filter(n_words != word) 
  colnames(n_words_df) = c(pterm)
  return(n_words_df)
  
}
```


## breaking corpus into administration and party buckets
```{r}
#by administration
bush_first_corpus <- corpus_subset(fed_corpus, presidential_term == "Bush-1") 
bush_second_corpus <-corpus_subset(fed_corpus, presidential_term == "Bush-2") 
obama_first_corpus <- corpus_subset(fed_corpus, presidential_term == "Obama-1") 
obama_second_corpus <- corpus_subset(fed_corpus, presidential_term == "Obama-2") 
trump_corpus <- corpus_subset(fed_corpus, presidential_term == "Trump-1" | presidential_term == "Trump-2") 
biden_corpus <- corpus_subset(fed_corpus, presidential_term == "Biden") 



```

## tokenizing/prepping subsets of data for word embeddings


```{r}



bush_1_toks_feats = prepping_tokens_we(bush_first_corpus, remove_words, 5, 0.99)
bush_2_toks_feats = prepping_tokens_we(bush_second_corpus, remove_words, 5, 0.99)
obama_1_toks_feats = prepping_tokens_we(obama_first_corpus, remove_words, 5, 0.99)
obama_2_toks_feats = prepping_tokens_we(obama_second_corpus, remove_words, 5, 0.99)
trump_toks_feats = prepping_tokens_we(trump_corpus, remove_words, 5, 0.99)
biden_toks_feats = prepping_tokens_we(biden_corpus, remove_words, 5, 0.99)

#head(obama_1_toks_feats)



```

#saving token files 
```{r}

saveRDS(bush_1_toks_feats, file = "token_files/bush_1_toks_feats.rds")
saveRDS(bush_2_toks_feats, file = "token_files/bush_2_toks_feats.rds")
saveRDS(obama_1_toks_feats, file = "token_files/obama_1_toks_feats.rds")
saveRDS(obama_2_toks_feats, file = "token_files/obama_2_toks_feats.rds")
saveRDS(trump_toks_feats, file = "token_files/trump_toks_feats.rds")
saveRDS(biden_toks_feats, file = "token_files/biden_toks_feats.rds")

```

##create glove word embeddings
#start here if working with token object files
```{r}
# Construct the feature co-occurrence matrix for our tokens object

#bush_1_toks_feats = readRDS("token_files/bush_1_toks_feats.rds")
#bush_2_toks_feats = readRDS("token_files/bush_2_toks_feats.rds")
#obama_1_toks_feats = readRDS("token_files/obama_1_toks_feats.rds")
#obama_2_toks_feats = readRDS("token_files/obama_2_toks_feats.rds")
#trump_toks_feats = readRDS("token_files/trump_toks_feats.rds")
#biden_toks_feats = readRDS("token_files/biden_toks_feats.rds")

obama_1_glove_results = glove_modeling(obama_1_toks_feats, 300, 5, "frequency", 12)

obama_2_glove_results = glove_modeling(obama_2_toks_feats, 300, 5, "frequency",12)

bush_1_glove_results = glove_modeling(bush_1_toks_feats, 300, 5, "frequency",12)

bush_2_glove_results = glove_modeling(bush_2_toks_feats, 300, 5, "frequency",12)

trump_glove_results = glove_modeling(trump_toks_feats, 300, 5, "frequency", 12)

biden_glove_results = glove_modeling(biden_toks_feats, 300, 5, "frequency", 12)

saveRDS(obama_1_glove_results, file = "glove_models/obama_1_glove_results.rds")
saveRDS(obama_2_glove_results, file = "glove_models/obama_2_glove_results.rds")
saveRDS(bush_1_glove_results, file = "glove_models/bush_1_glove_results.rds")
saveRDS(bush_2_glove_results, file = "glove_models/bush_2_glove_results.rds")
saveRDS(trump_glove_results, file = "glove_models/trump_glove_results.rds")
saveRDS(biden_glove_results, file = "glove_models/biden_glove_results.rds")


# features?
#head(rownames(obama_1_glove_results))

#class(obama_1_glove_results)



#weighted versions


obama_1_glove_results_wt = glove_modeling(obama_1_toks_feats, 300, 5, "weighted", 12)

obama_2_glove_results_wt = glove_modeling(obama_2_toks_feats, 300, 5, "weighted",12)

bush_1_glove_results_wt = glove_modeling(bush_1_toks_feats, 300, 5, "weighted",12)

bush_2_glove_results_wt = glove_modeling(bush_2_toks_feats, 300, 5, "weighted",12)

trump_glove_results_wt = glove_modeling(trump_toks_feats, 300, 5, "weighted", 12)

biden_glove_results_wt = glove_modeling(biden_toks_feats, 300, 5, "weighted", 12)

saveRDS(obama_1_glove_results_wt, file = "glove_models/obama_1_glove_results_wt.rds")
saveRDS(obama_2_glove_results_wt, file = "glove_models/obama_2_glove_results_wt.rds")
saveRDS(bush_1_glove_results_wt, file = "glove_models/bush_1_glove_results_wt.rds")
saveRDS(bush_2_glove_results_wt, file = "glove_models/bush_2_glove_results_wt.rds")
saveRDS(trump_glove_results_wt, file = "glove_models/trump_glove_results_wt.rds")
saveRDS(biden_glove_results_wt, file = "glove_models/biden_glove_results_wt.rds")

```


loading pretrained globe model as comparison
```{r}

# ---------- 1. Prepare the pretrained embedding

# Download Glove here: GloVe pretrained (https://nlp.stanford.edu/projects/glove/)
# data table is faster than read_delim
#file is glove model trained on 6 billion words in 300 dimensions
glove_wts <- data.table::fread("glove.6B.300d.txt", quote = "", data.table = FALSE) %>% 
  as_tibble()

# convert to matrix
glove_matrix <- as.matrix(glove_wts %>% select(-V1))

# add names
rownames(glove_matrix) <- glove_wts$V1

# check object
#head(glove_matrix)
dim(glove_matrix)
#glove_matrix["war", ]

```

comparing results
```{r}

#finding nearest neighbor words based on cosine similarity



bush1_data_embedding = find_nearest("data", bush_1_glove_results, 20, "Bush-1")
bush2_data_embedding = find_nearest("data", bush_2_glove_results, 20, "Bush-2")
obama1_data_embedding = find_nearest("data", obama_1_glove_results, 20, "Obama-1")
obama2_data_embedding = find_nearest("data", obama_2_glove_results, 20, "Obama-2")
trump_data_embedding = find_nearest("data", trump_glove_results, 20, "Trump")
biden_data_embedding = find_nearest("data", biden_glove_results, 20, "Biden")
glove_data_embedding = find_nearest("data", glove_matrix, 20, "Glove")

all_terms_data_embedding = cbind(bush1_data_embedding, bush2_data_embedding, obama1_data_embedding,
                                 obama2_data_embedding, trump_data_embedding, biden_data_embedding, 
                                 glove_data_embedding)

write.csv(all_terms_data_embedding, "results/pterm_data_nn.csv", row.names = FALSE)

bush1_eval_embedding = find_nearest("evaluation", bush_1_glove_results, 20, "Bush-1")
bush2_eval_embedding = find_nearest("evaluation", bush_2_glove_results, 20, "Bush-2")
obama1_eval_embedding = find_nearest("evaluation", obama_1_glove_results, 20, "Obama-1")
obama2_eval_embedding = find_nearest("evaluation", obama_2_glove_results, 20, "Obama-2")
trump_eval_embedding = find_nearest("evaluation", trump_glove_results, 20, "Trump")
biden_eval_embedding = find_nearest("evaluation", biden_glove_results, 20, "Biden")
glove_eval_embedding = find_nearest("evaluation", glove_matrix, 20, "Glove")

all_terms_eval_embedding = cbind(bush1_eval_embedding, bush2_eval_embedding, obama1_eval_embedding,
                                 obama2_eval_embedding, trump_eval_embedding, biden_eval_embedding, 
                                 glove_eval_embedding)

write.csv(all_terms_eval_embedding, "results/pterm_eval_nn.csv", row.names = FALSE)

bush1_analysis_embedding = find_nearest("analysis", bush_1_glove_results, 20, "Bush-1")
bush2_analysis_embedding = find_nearest("analysis", bush_2_glove_results, 20, "Bush-2")
obama1_analysis_embedding = find_nearest("analysis", obama_1_glove_results, 20, "Obama-1")
obama2_analysis_embedding = find_nearest("analysis", obama_2_glove_results, 20, "Obama-2")
trump_analysis_embedding = find_nearest("analysis", trump_glove_results, 20, "Trump")
biden_analysis_embedding = find_nearest("analysis", biden_glove_results, 20, "Biden")
glove_analysis_embedding = find_nearest("analysis", glove_matrix, 20, "Glove")

all_terms_analysis_embedding = cbind(bush1_analysis_embedding, bush2_analysis_embedding, obama1_analysis_embedding,
                                 obama2_analysis_embedding, trump_analysis_embedding, biden_analysis_embedding, 
                                 glove_analysis_embedding)

write.csv(all_terms_analysis_embedding, "results/pterm_analysis_nn.csv", row.names = FALSE)


bush1_eff_embedding = find_nearest("efficiency", bush_1_glove_results, 20, "Bush-1")
bush2_eff_embedding = find_nearest("efficiency", bush_2_glove_results, 20, "Bush-2")
obama1_eff_embedding = find_nearest("efficiency", obama_1_glove_results, 20, "Obama-1")
obama2_eff_embedding = find_nearest("efficiency", obama_2_glove_results, 20, "Obama-2")
trump_eff_embedding = find_nearest("efficiency", trump_glove_results, 20, "Trump")
biden_eff_embedding = find_nearest("efficiency", biden_glove_results, 20, "Biden")
glove_eff_embedding = find_nearest("efficiency", glove_matrix, 20, "Glove")

all_terms_eff_embedding = cbind(bush1_eff_embedding, bush2_eff_embedding, obama1_eff_embedding,
                                 obama2_eff_embedding, trump_eff_embedding, biden_eff_embedding, 
                                 glove_eff_embedding)

write.csv(all_terms_eff_embedding, "results/pterm_efficiency_nn.csv", row.names = FALSE)
```

weighted versions of embedding model

```{r}

bush1_data_embedding_wt = find_nearest("data", bush_1_glove_results_wt, 20, "Bush-1")
bush2_data_embedding_wt = find_nearest("data", bush_2_glove_results_wt, 20, "Bush-2")
obama1_data_embedding_wt = find_nearest("data", obama_1_glove_results_wt, 20, "Obama-1")
obama2_data_embedding_wt = find_nearest("data", obama_2_glove_results_wt, 20, "Obama-2")
trump_data_embedding_wt = find_nearest("data", trump_glove_results_wt, 20, "Trump")
biden_data_embedding_wt = find_nearest("data", biden_glove_results_wt, 20, "Biden")
glove_data_embedding = find_nearest("data", glove_matrix, 20, "Glove")

all_terms_data_embedding_wt = cbind(bush1_data_embedding_wt, bush2_data_embedding_wt, obama1_data_embedding_wt,
                                 obama2_data_embedding_wt, trump_data_embedding_wt, biden_data_embedding_wt, 
                                 glove_data_embedding)

write.csv(all_terms_data_embedding_wt, "results/pterm_data_nn_weighted.csv", row.names = FALSE)

bush1_eval_embedding_wt = find_nearest("evaluation", bush_1_glove_results_wt, 20, "Bush-1")
bush2_eval_embedding_wt = find_nearest("evaluation", bush_2_glove_results_wt, 20, "Bush-2")
obama1_eval_embedding_wt = find_nearest("evaluation", obama_1_glove_results_wt, 20, "Obama-1")
obama2_eval_embedding_wt = find_nearest("evaluation", obama_2_glove_results_wt, 20, "Obama-2")
trump_eval_embedding_wt = find_nearest("evaluation", trump_glove_results_wt, 20, "Trump")
biden_eval_embedding_wt = find_nearest("evaluation", biden_glove_results_wt, 20, "Biden")
glove_eval_embedding = find_nearest("evaluation", glove_matrix, 20, "Glove")

all_terms_eval_embedding_wt = cbind(bush1_eval_embedding_wt, bush2_eval_embedding_wt, obama1_eval_embedding_wt,
                                 obama2_eval_embedding_wt, trump_eval_embedding_wt, biden_eval_embedding_wt, 
                                 glove_eval_embedding)

write.csv(all_terms_eval_embedding_wt, "results/pterm_eval_nn_weighted.csv", row.names = FALSE)

bush1_analysis_embedding_wt = find_nearest("analysis", bush_1_glove_results_wt, 20, "Bush-1")
bush2_analysis_embedding_wt = find_nearest("analysis", bush_2_glove_results_wt, 20, "Bush-2")
obama1_analysis_embedding_wt = find_nearest("analysis", obama_1_glove_results_wt, 20, "Obama-1")
obama2_analysis_embedding_wt = find_nearest("analysis", obama_2_glove_results_wt, 20, "Obama-2")
trump_analysis_embedding_wt = find_nearest("analysis", trump_glove_results_wt, 20, "Trump")
biden_analysis_embedding_wt = find_nearest("analysis", biden_glove_results_wt, 20, "Biden")
glove_analysis_embedding = find_nearest("analysis", glove_matrix, 20, "Glove")

all_terms_analysis_embedding_wt = cbind(bush1_analysis_embedding_wt, bush2_analysis_embedding_wt, obama1_analysis_embedding_wt,
                                 obama2_analysis_embedding_wt, trump_analysis_embedding_wt, biden_analysis_embedding_wt, 
                                 glove_analysis_embedding)

write.csv(all_terms_analysis_embedding_wt, "results/pterm_analysis_nn_weighted.csv", row.names = FALSE)

bush1_eff_embedding_wt = find_nearest("efficiency", bush_1_glove_results_wt, 20, "Bush-1")
bush2_eff_embedding_wt = find_nearest("efficiency", bush_2_glove_results_wt, 20, "Bush-2")
obama1_eff_embedding_wt = find_nearest("efficiency", obama_1_glove_results_wt, 20, "Obama-1")
obama2_eff_embedding_wt = find_nearest("efficiency", obama_2_glove_results_wt, 20, "Obama-2")
trump_eff_embedding_wt = find_nearest("efficiency", trump_glove_results_wt, 20, "Trump")
biden_eff_embedding_wt = find_nearest("efficiency", biden_glove_results_wt, 20, "Biden")
glove_eff_embedding = find_nearest("efficiency", glove_matrix, 20, "Glove")

all_terms_eff_embedding_wt = cbind(bush1_eff_embedding_wt, bush2_eff_embedding_wt, obama1_eff_embedding_wt,
                                 obama2_eff_embedding_wt, trump_eff_embedding_wt, biden_eff_embedding_wt, 
                                 glove_eff_embedding)

write.csv(all_terms_eff_embedding_wt, "results/pterm_efficiency_nn_weighted.csv", row.names = FALSE)

```

### party level analysis

```{r}

#by party

republican_corpus <- corpus_subset(fed_corpus, pres_party == "republican")
democrat_corpus <- corpus_subset(fed_corpus, pres_party == "democrat")

```

## looking at unigrams - no bigrams in model 
```{r}

dem_toks_feats = prepping_tokens_we(democrat_corpus, remove_words, 5, 0.99)
rep_toks_feats = prepping_tokens_we(republican_corpus, remove_words, 5, 0.99)

saveRDS(dem_toks_feats, file = "token_files/dem_toks_feats.rds")
saveRDS(rep_toks_feats, file = "token_files/rep_toks_feats.rds")

#dem_toks_feats = readRDS("token_files/dem_toks_feats.rds")
#rep_toks_feats = readRDS("token_files/rep_toks_feats.rds")

dem_glove_results = glove_modeling(dem_toks_feats, 300, 5, "frequency", 12)
rep_glove_results = glove_modeling(rep_toks_feats, 300, 5, "frequency",  12)

dem_glove_results_wt = glove_modeling(dem_toks_feats, 300, 5, "weighted", 12)
rep_glove_results_wt = glove_modeling(rep_toks_feats, 300, 5, "weighted",  12)

saveRDS(dem_glove_results, file = "glove_models/dem_glove_results.rds")
saveRDS(rep_glove_results, file = "glove_models/rep_glove_results.rds")
saveRDS(dem_glove_results_wt, file = "glove_models/dem_glove_results_wt.rds")
saveRDS(rep_glove_results_wt, file = "glove_models/rep_glove_results_wt.rds")




```

```{r}

#data
dem_data_embedding = find_nearest("data", dem_glove_results, 20, "Dem")
rep_data_embedding = find_nearest("data", rep_glove_results, 20, "Rep")

dem_data_embedding_wt = find_nearest("data", dem_glove_results_wt, 20, "Dem-WT")
rep_data_embedding_wt = find_nearest("data", rep_glove_results_wt, 20, "Rep-WT")

party_data_embedding = cbind(dem_data_embedding, rep_data_embedding, dem_data_embedding_wt, rep_data_embedding_wt)

write.csv(party_data_embedding, "results/party_data_nn.csv", row.names = FALSE)

#eval
dem_eval_embedding = find_nearest("evaluation", dem_glove_results, 20, "Dem")
rep_eval_embedding = find_nearest("evaluation", rep_glove_results, 20, "Rep")

dem_eval_embedding_wt = find_nearest("evaluation", dem_glove_results_wt, 20, "Dem-WT")
rep_eval_embedding_wt = find_nearest("evaluation", rep_glove_results_wt, 20, "Rep-WT")

party_eval_embedding = cbind(dem_eval_embedding, rep_eval_embedding, dem_eval_embedding_wt, rep_eval_embedding_wt)

write.csv(party_eval_embedding, "results/party_eval_nn.csv", row.names = FALSE)


#efficiency

dem_eff_embedding = find_nearest("efficiency", dem_glove_results, 20, "Dem")
rep_eff_embedding = find_nearest("efficiency", rep_glove_results, 20, "Rep")

dem_eff_embedding_wt = find_nearest("efficiency", dem_glove_results_wt, 20, "Dem-WT")
rep_eff_embedding_wt = find_nearest("efficiency", rep_glove_results_wt, 20, "Rep-WT")

party_eff_embedding = cbind(dem_eff_embedding, rep_eff_embedding, dem_eff_embedding_wt, rep_eff_embedding_wt)

write.csv(party_eff_embedding, "results/party_eff_nn.csv", row.names = FALSE)

#analysis

dem_analysis_embedding = find_nearest("analysis", dem_glove_results, 20, "Dem")
rep_analysis_embedding = find_nearest("analysis", rep_glove_results, 20, "Rep")

dem_analysis_embedding_wt = find_nearest("analysis", dem_glove_results_wt, 20, "Dem-WT")
rep_analysis_embedding_wt = find_nearest("analysis", rep_glove_results_wt, 20, "Rep-WT")

party_analysis_embedding = cbind(dem_analysis_embedding, rep_analysis_embedding, dem_analysis_embedding_wt, rep_analysis_embedding_wt)

write.csv(party_analysis_embedding, "results/party_analysis_nn.csv", row.names = FALSE)

#ai - results are not meaningful/related to fish
dem_ai_embedding = find_nearest("ai", dem_glove_results, 20, "Dem")
rep_ai_embedding = find_nearest("ai", rep_glove_results, 20, "Rep")

dem_ai_embedding_wt = find_nearest("ai", dem_glove_results_wt, 20, "Dem-WT")
rep_ai_embedding_wt = find_nearest("ai", rep_glove_results_wt, 20, "Rep-WT")

party_ai_embedding = cbind(dem_ai_embedding, rep_ai_embedding, dem_ai_embedding_wt, rep_ai_embedding_wt)


```

## adding bigrams to tokens used in word embedding model

```{r}

prepping_tokens_we_bigrams = function(c, words_to_remove, mtf, mdf, bigrams){
  t = tokens(c, what = "word", remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_separators = TRUE) %>% tokens_tolower() %>% tokens_remove(pattern = junk_patterns, valuetype = "regex") %>% tokens_compound(pattern = bigrams)
  f = dfm(t, verbose = FALSE) %>% 
  dfm_remove(c(stopwords(language = "en"), words_to_remove)) %>% 
  dfm_trim(min_termfreq = mtf, termfreq_type = "count", max_docfreq = mdf, docfreq_type = "prop") %>%
  featnames() 
  
  tokens_pad = tokens_select(t,
                            f,
                            padding = TRUE)
  return(tokens_pad)
}

custom_bigrams <- phrase(c("data analysis", 
                           "data collection",
                           "program evaluation",
                           "performance evaluation",
                           "artificial intelligence",
                           "fuel efficiency",
                           "energy efficiency"))

dem_toks_feats_bigrams = prepping_tokens_we_bigrams(democrat_corpus, remove_words, 5, 0.99, custom_bigrams)
rep_toks_feats_bigrams = prepping_tokens_we_bigrams(republican_corpus, remove_words, 5, 0.99, custom_bigrams)

saveRDS(dem_toks_feats_bigrams, file = "token_files/dem_toks_feats_bigrams.rds")
saveRDS(rep_toks_feats_bigrams, file = "token_files/rep_toks_feats_bigrams.rds")

#dem_toks_feats_bigrams= readRDS("token_files/dem_toks_feats_bigrams.rds")
#rep_toks_feats_bigrams = readRDS("token_files/rep_toks_feats_bigrams.rds")


dem_glove_results_bigrams = glove_modeling(dem_toks_feats_bigrams, 300, 5, "frequency", 10)
rep_glove_results_bigrams = glove_modeling(rep_toks_feats_bigrams, 300, 5, "frequency",  10)

saveRDS(dem_glove_results_bigrams, file = "glove_models/dem_glove_results_bigrams.rds")
saveRDS(rep_glove_results_bigrams, file = "glove_models/rep_glove_results_bigrams.rds")

dem_glove_results_bigrams_wt = glove_modeling(dem_toks_feats_bigrams, 300, 5, "weighted", 10)
rep_glove_results_bigrams_wt = glove_modeling(rep_toks_feats_bigrams, 300, 5, "weighted",  10)


saveRDS(dem_glove_results_bigrams_wt, file = "glove_models/dem_glove_results_bigrams_wt.rds")
saveRDS(rep_glove_results_bigrams_wt, file = "glove_models/rep_glove_results_bigrams_wt.rds")


```

```{r}

dem_data_embedding_bigrams = find_nearest("data", dem_glove_results_bigrams, 20, "Dem_data")
rep_data_embedding_bigrams = find_nearest("data", rep_glove_results_bigrams, 20, "Rep_data")

dem_analysis_embedding_bigrams = find_nearest("analysis", dem_glove_results_bigrams, 20, "Dem_analysis")
rep_analysis_embedding_bigrams = find_nearest("analysis", rep_glove_results_bigrams, 20, "Rep_analysis")

dem_da_embedding_bigrams = find_nearest("data_analysis", dem_glove_results_bigrams, 20, "Dem_da")
rep_da_embedding_bigrams = find_nearest("data_analysis", rep_glove_results_bigrams, 20, "Rep_da")

dem_dc_embedding_bigrams = find_nearest("data_collection", dem_glove_results_bigrams, 20, "Dem_dc")
rep_dc_embedding_bigrams = find_nearest("data_collection", rep_glove_results_bigrams, 20, "Rep_dc")

party_da_embedding = cbind(dem_data_embedding_bigrams, rep_data_embedding_bigrams, dem_analysis_embedding_bigrams, rep_analysis_embedding_bigrams, dem_da_embedding_bigrams, rep_da_embedding_bigrams, dem_dc_embedding_bigrams, rep_dc_embedding_bigrams)

write.csv(party_da_embedding, "results/party_data_embedding_bigrams.csv", row.names = FALSE)

dem_eval_embedding_bigrams = find_nearest("evaluation", dem_glove_results_bigrams, 20, "Dem-eval")
rep_eval_embedding_bigrams = find_nearest("evaluation", rep_glove_results_bigrams, 20, "Rep-eval")

#dem_progeval_embedding_bigrams = find_nearest("program_evaluation", dem_glove_results_bigrams, 20, "Dem-progeval")
#rep_progeval_embedding_bigrams = find_nearest("program_evaluation", rep_glove_results_bigrams, 20, "Rep-progeval")

dem_perfeval_embedding_bigrams = find_nearest("performance_evaluation", dem_glove_results_bigrams, 20, "Dem-perfeval")
rep_perfeval_embedding_bigrams = find_nearest("performance_evaluation", rep_glove_results_bigrams, 20, "Rep-perfeval")

#program evaluation does not provide meaningful results, removing from results
party_eval_embedding = cbind(dem_eval_embedding_bigrams, rep_eval_embedding_bigrams, dem_perfeval_embedding_bigrams, rep_perfeval_embedding_bigrams)

write.csv(party_eval_embedding, "results/party_eval_embedding_bigrams.csv", row.names = FALSE)


dem_eff_embedding_bigrams = find_nearest("efficiency", dem_glove_results_bigrams, 20, "Dem")
rep_eff_embedding_bigrams = find_nearest("efficiency", rep_glove_results_bigrams, 20, "Rep")

party_eff_embedding_nobigrams = cbind(dem_eff_embedding_bigrams, rep_eff_embedding_bigrams)

write.csv(party_eff_embedding_nobigrams, "results/party_eff_embedding_nobigrams.csv", row.names = FALSE)


dem_ai_embedding_bigrams = find_nearest("artificial_intelligence", dem_glove_results_bigrams, 20, "Dem")
rep_ai_embedding_bigrams = find_nearest("artificial_intelligence", rep_glove_results_bigrams, 20, "Rep")

party_ai_embedding = cbind(dem_ai_embedding_bigrams, rep_ai_embedding_bigrams)

write.csv(party_ai_embedding , "results/party_ai_embedding.csv", row.names = FALSE)


```

weighted version
```{r}

dem_data_embedding_bigrams_wt = find_nearest("data", dem_glove_results_bigrams_wt, 20, "Dem_data_wt")
rep_data_embedding_bigrams_wt = find_nearest("data", rep_glove_results_bigrams_wt, 20, "Rep_data_wt")

dem_analysis_embedding_bigrams_wt = find_nearest("analysis", dem_glove_results_bigrams_wt, 20, "Dem_analysis_wt")
rep_analysis_embedding_bigrams_wt = find_nearest("analysis", rep_glove_results_bigrams_wt, 20, "Rep_analysis_wt")

dem_da_embedding_bigrams_wt = find_nearest("data_analysis", dem_glove_results_bigrams_wt, 20, "Dem_da_wt")
rep_da_embedding_bigrams_wt = find_nearest("data_analysis", rep_glove_results_bigrams_wt, 20, "Rep_da_wt")

dem_dc_embedding_bigrams_wt = find_nearest("data_collection", dem_glove_results_bigrams_wt, 20, "Dem_dc_wt")
rep_dc_embedding_bigrams_wt = find_nearest("data_collection", rep_glove_results_bigrams_wt, 20, "Rep_dc_wt")

party_data_embedding_wt = cbind(dem_data_embedding_bigrams_wt, rep_data_embedding_bigrams_wt, dem_analysis_embedding_bigrams_wt, rep_analysis_embedding_bigrams_wt, dem_da_embedding_bigrams_wt, rep_da_embedding_bigrams_wt, dem_dc_embedding_bigrams_wt, rep_dc_embedding_bigrams_wt)

write.csv(party_data_embedding_wt, "results/party_data_embedding_bigrams_wt.csv", row.names = FALSE)

dem_eval_embedding_bigrams_wt = find_nearest("evaluation", dem_glove_results_bigrams_wt, 20, "Dem-eval-wt")
rep_eval_embedding_bigrams_wt = find_nearest("evaluation", rep_glove_results_bigrams_wt, 20, "Rep-eval-wt")

#dem_progeval_embedding_bigrams_wt = find_nearest("program_evaluation", dem_glove_results_bigrams_wt, 20, "Dem-progeval")
#rep_progeval_embedding_bigrams_wt = find_nearest("program_evaluation", rep_glove_results_bigrams_wt, 20, "Rep-progeval")

dem_perfeval_embedding_bigrams_wt = find_nearest("performance_evaluation", dem_glove_results_bigrams_wt, 20, "Dem-perfeval-wt")
rep_perfeval_embedding_bigrams_wt = find_nearest("performance_evaluation", rep_glove_results_bigrams_wt, 20, "Rep-perfeval-wt")

#program evaluation does not provide meaningful results, removing from results
party_eval_embedding_wt = cbind(dem_eval_embedding_bigrams_wt, rep_eval_embedding_bigrams_wt, dem_perfeval_embedding_bigrams_wt, rep_perfeval_embedding_bigrams_wt)

write.csv(party_eval_embedding_wt, "results/party_eval_embedding_bigrams_wt.csv", row.names = FALSE)


dem_eff_embedding_bigrams_wt = find_nearest("efficiency", dem_glove_results_bigrams_wt, 20, "Dem-wt")
rep_eff_embedding_bigrams_wt = find_nearest("efficiency", rep_glove_results_bigrams_wt, 20, "Rep-wt")

party_eff_embedding_nobigrams_wt = cbind(dem_eff_embedding_bigrams_wt, rep_eff_embedding_bigrams_wt)

write.csv(party_eff_embedding_nobigrams_wt, "results/party_eff_embedding_nobigrams_wt.csv", row.names = FALSE)


dem_ai_embedding_bigrams_wt = find_nearest("artificial_intelligence", dem_glove_results_bigrams_wt, 20, "Dem-wt")
rep_ai_embedding_bigrams_wt = find_nearest("artificial_intelligence", rep_glove_results_bigrams_wt, 20, "Rep-wt")

party_ai_embedding_wt = cbind(dem_ai_embedding_bigrams_wt, rep_ai_embedding_bigrams_wt)

write.csv(party_ai_embedding_wt , "results/party_ai_embedding_wt.csv", row.names = FALSE)


```


combining results:

```{r}

party_da_embedding_v2 = cbind(party_da_embedding, party_data_embedding_wt)

party_eff_embedding_nobigrams_v2 = cbind(party_eff_embedding_nobigrams, party_eff_embedding_nobigrams_wt)

party_eval_embedding_v2 = cbind(party_eval_embedding, party_eval_embedding_wt)

party_ai_embedding_v2 = cbind(party_ai_embedding, party_ai_embedding_wt)


write.csv(party_da_embedding_v2, "results/party_da_embedding_v2.csv", row.names = FALSE)
write.csv(party_eff_embedding_nobigrams_v2, "results/party_eff_embedding_nobigrams_v2.csv", row.names = FALSE)
write.csv(party_eval_embedding_v2, "results/party_eval_embedding_v2.csv", row.names = FALSE)
write.csv(party_ai_embedding_v2, "results_party_ai_embedding_v2.csv", row.names = FALSE)

```

Full Corpus

unable to create Glove model - not enough memory for full corpus

```{r}

fed_corpus_tokens = readRDS("token_files/fed_corpus_tokens.rds")

fed_corpus_tok_dfm = fed_corpus_tokens %>% dfm() %>% dfm_remove(c(stopwords(language = "en"), remove_words)) %>% dfm_trim(min_termfreq = 20, termfreq_type = "count",max_docfreq = 0.99, docfreq_type = "prop") %>% featnames()

fed_tokens_pad = tokens_select(fed_corpus_tokens,
                            fed_corpus_tok_dfm,
                            padding = TRUE)

#fed_glove_results = glove_modeling(fed_tokens_pad, 200, 5, "frequency", 12)

```